Toward dynamic models of combat or lack thereof in animal mating

### 2016-03-14 ms.tex
old data cleanup and scrap changes
results section fixed

\newcommand{\smurl}[1]{{\footnotesize\url{#1}}}
\usepackage{graphicx}

@@

This means adding some normally distributed noise with $\mu = 0$ and $\sigma$ varying from trait to trait.

@@

\section{Results} % (fold)
\label{sec:results}
% energy expenditure plots
\begin{figure}[h!]
    \centering
    \includegraphics[width=10cm,height=10cm,keepaspectratio]{figures/energy_pc_plot_exp_f15.pdf}
    \caption{Linear commitment function, ftime = 10. Percent energy expenditure of cohort at generation 499}
    \label{fig:var energy pc}
    \centering

    \includegraphics[width=10cm,height=10cm,keepaspectratio]{figures/energy_total_plot_exp_f15.pdf}
    \caption{Linear commitment function, ftime = 10. Total energy expenditure of cohort at generation 499}
    \label{fig:var energy total}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=10cm,height=10cm,keepaspectratio]{figures/exp_f15_k_density.pdf}
    \caption{Linear commitment function, ftime = 10. a density plot of the aggression parameter k}
    \label{fig:k density}

    \includegraphics[width=10cm,height=10cm,keepaspectratio]{figures/exp_f15_e_0_density.pdf}
    \caption{Linear commitment function, ftime = 10. a density plot of the aggression parameter $e_0$.}
    \label{fig:e_0 density}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=10cm,height=10cm,keepaspectratio]{figures/exp_f15_k_history.pdf}
    \caption{Linear commitment function, ftime = 10. $k$ the grey bounds are the standard deviation}

    \includegraphics[width=10cm,height=10cm,keepaspectratio]{figures/exp_f15_e_0_history.pdf}
    \caption{Linear commitment function, ftime = 10 $e_0$ the grey bounds are the standard deviation}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=15cm,height=10cm,keepaspectratio]{figures/lin_f10_num_winners.pdf}
    \caption{Linear commitment function, ftime = 10 Number of successful males at different patch areas}
    \label{fig:num winners expf10}
\end{figure}

@@

% "maturation_center":4,
% "maturation_width":1,
% "growth_param_a":0.5,
% "growth_param_b":0.1,
% "initial_mass":5,
% "mass_to_energy":10.0,
% "search_energy_coef":5,
% "mutation_rate":0.1,
% "mutation_sd":0.1
% "stability_cutoff": 0.01,
% "stability_lag":50

\section{Figures}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=15cm,keepaspectratio]{figures/area_searched}
\caption{the area searched by a male in interval $dt$}
\label{fig:area searched figure}
\end{figure}
\clearpage

>>>>

\newcommand{\smurl}[1]{{\footnotesize\url{#1}}}

\newcommand{\myfigure}[4]{
\begin{figure}[h!]
    \centering
    \includegraphics[width=10cm,height=9cm,keepaspectratio]{#1}
    \caption{#2}
    \centering
    \includegraphics[width=10cm,height=9cm,keepaspectratio]{#3}
    \caption{#4}
\end{figure}
}

\usepackage{graphicx}

@@

This means a chance to add some normally distributed noise with $\mu = 0$ and small $\sigma$.

@@

\section{Results} % (fold)
\label{sec:results}

\myfigure{figures/energy_pc_plot_cm_100.pdf}{pc energy spent on what}{figures/energy_total_plot_cm_100.pdf}{total energy spent on what}

\myfigure{figures/e_0_nest_density.pdf}{e 0 with patch area}{figures/k_patch_area.pdf}{k with patch area}

\myfigure{figures/e_0_nest_density.pdf}{e 0 with nest density}{figures/k_patch_area.pdf}{k with nest density}

\begin{figure}[h!]
    \centering
    \includegraphics[width=15cm,height=10cm,keepaspectratio]{figures/cm_100_num_winners.pdf}
    \caption{Number of successful males at different patch areas}
\end{figure}

@@
